Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-27 Report/convergence_centralized.tex
modified in linux

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\allowdisplaybreaks{\begin{multline}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{multline}}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective value sequence as
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
\end{equation*}
Note that the feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration. Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.

@@

Now, to claim the convergence of transmit precoders and receive beamformers, we need to show the uniqueness in the mapping between the transmit and receive beamformers to the objective function. The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, can be attributed to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}. The linearized \eqref{eqn-8} can be written as
\begin{multline} \label{uniqueness-1}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and the \ac{MSE} expression as
\begin{multline} \label{uniqueness-2}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is unique for the given set of transmit precoders. It is due to the constraints \eqref{uniqueness-1} and \eqref{uniqueness-2}, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.

>>>>

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\allowdisplaybreaks{\begin{multline}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{multline}}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective value sequence as
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
\end{equation*}
The feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration. Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.

@@

To prove the convergence of the transmit and the receive beamformers, we use the uniqueness in the mapping between the transmit and receive beamformers with respect to the objective function. The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, is achieved due to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}. The linearized \eqref{eqn-8} can be written as
\begin{multline} \label{uniqueness-1}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for \ac{MSE} expression as
\begin{multline} \label{uniqueness-2}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is unique for the given set of transmit precoders. It is due to the constraints \eqref{uniqueness-1} and \eqref{uniqueness-2}, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.

### 2015-02-27 Report/ieee_journal.tex
modified in linux

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

>>>>

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
